Effect of quality-adjusted production function inputs

### 2015-07-07 Articles/Presentation_ESEE_2015/ESEE_2015.Rnw
Removing y axis ticks.

<<Factor_shares_bar_graph_function>>=
fsbg <- function(coun, mod){
  bar_chart_data <- filter(AllCoeffs, Country==coun & model==mod) %>% 
    select(Country, model, flavor, energy, nest, cst, alpha_1, alpha_2, alpha_3)
  # Change boolean cst column to meaningful words
  bar_chart_data$cst <- plyr::mapvalues(bar_chart_data$cst, from=c(TRUE, FALSE), to=c("Adhere to CST", "Reject CST"))
  # Change nest to a nicer-looking nest string
  bar_chart_data$nest <- plyr::mapvalues(bar_chart_data$nest, 
                                         from=c("kl", "kle", "lek", "ekl"), 
                                         to=c("(kl)", "(kl)e", "(le)k", "(ek)l"))
  # Add a label column
  bar_chart_data$label <- paste(bar_chart_data$cst, bar_chart_data$flavor, 
                                bar_chart_data$energy, bar_chart_data$nest, sep=", ")
  # Capture the order that we want for the models on the vertical axis.
  order <- bar_chart_data$label
  # Now melt the data
  bar_chart_data <- melt(bar_chart_data, 
                         measure.vars = c("alpha_1", "alpha_2", "alpha_3"), 
                         value.name = "value", 
                         variable.name = "variable")
  # Define the color palette (see http://www.cookbook-r.com/Graphs/Colors_(ggplot2))
  cbPalette <- c("#E69F00", "#999999", "#F0E442", "#56B4E9", "#009E73", "#0072B2", "#D55E00", "#CC79A7")
  # Make the plot
  plot <- ggplot(bar_chart_data, mapping=aes(x=label, y=value, fill=variable, width=0.4)) + 
    geom_bar(stat="identity") + 
    xlab("") +
    scale_x_discrete(limits=rev(order)) +
    ylab("") +
    scale_y_continuous(breaks=c(0, 0.5, 1)) + 
    guides(fill=guide_legend(title=NULL)) +
    coord_flip() + 
    scale_fill_brewer(palette="OrRd") +
    xy_theme()
  return(plot)
}
@

>>>>

<<Factor_shares_bar_graph_function>>=
fsbg <- function(coun, mod){
  bar_chart_data <- filter(AllCoeffs, Country==coun & model==mod) %>% 
    select(Country, model, flavor, energy, nest, cst, alpha_1, alpha_2, alpha_3)
  # Change boolean cst column to meaningful words
  bar_chart_data$cst <- plyr::mapvalues(bar_chart_data$cst, from=c(TRUE, FALSE), to=c("Adhere to CST", "Reject CST"))
  # Change nest to a nicer-looking nest string
  bar_chart_data$nest <- plyr::mapvalues(bar_chart_data$nest, 
                                         from=c("kl", "kle", "lek", "ekl"), 
                                         to=c("(kl)", "(kl)e", "(le)k", "(ek)l"))
  # Add a label column
  bar_chart_data$label <- paste(bar_chart_data$cst, bar_chart_data$flavor, 
                                bar_chart_data$energy, bar_chart_data$nest, sep=", ")
  # Capture the order that we want for the models on the vertical axis.
  order <- bar_chart_data$label
  # Now melt the data
  bar_chart_data <- melt(bar_chart_data, 
                         measure.vars = c("alpha_1", "alpha_2", "alpha_3"), 
                         value.name = "value", 
                         variable.name = "variable")
  # Define the color palette (see http://www.cookbook-r.com/Graphs/Colors_(ggplot2))
  cbPalette <- c("#E69F00", "#999999", "#F0E442", "#56B4E9", "#009E73", "#0072B2", "#D55E00", "#CC79A7")
  # Make the plot
  plot <- ggplot(bar_chart_data, mapping=aes(x=label, y=value, fill=variable, width=0.4)) + 
    geom_bar(stat="identity") + 
    xlab("") +
    scale_x_discrete(limits=rev(order)) +
    ylab("") +
    scale_y_continuous(breaks=c(0, 0.5, 1)) + 
    guides(fill=guide_legend(title=NULL)) +
    coord_flip() + 
    scale_fill_brewer(palette="OrRd") +
    xy_theme() +
    theme(axis.ticks.y = element_blank())
  return(plot)
}
@
